### 2021-11-06 manuscript.Rmd
cleaning up repo

note: "\\clearpage"

author_note:

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set()
library(papaja)
library(beepr)
library(tidyverse)
library(ggplot2)
library(grid)
library(rpact)
library(pracma)
library(coda)
library(BayesFactor)
library(parallel)
library(metafor)
library(citr)
library(TOSTER)
library(BFDA)

@@

@@

## Acknowledgement
This manuscript was created using `r cite_r("r-refs.bib")`.

>>>>

#note: "\\clearpage"

author_note: |
  All simulation data, analysis code, and research materials have been made publicly available on the OSF and GitHub and can be accessed at [link] and [link].

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set()
library(papaja)
library(tidyverse)
library(ggplot2)
library(grid)
library(gridExtra)
library(rpact)
library(pracma)
library(coda)
library(BayesFactor)
library(parallel)
library(citr)
library(TOSTER)
library(BFDA)

@@

## Transparency and openness

All data, analysis code, and research materials are available at [link]. The study was not preregistered. This manuscript was created using `r cite_r("r-refs.bib")`.

@@
